Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-11 sections/correlated-sicm-and-fm.tex
Nashimoto auskommentiert. Ist das nicht wide-field?

The study of Nashimoto was showing that for the detection of secretory proteins, like the von 
Willebrand factor, it is not always necessary to label the protein. Even with SICM alone the 
detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
images \cite{Nashimoto2015}.

>>>>

%% Wenn ich das Paper richtig verstehe, wurde hier aber kein konfokales FM
%% genutzt, oder? 
%
% Nashimoto et al. investigated whether the secretion of the von 
% Willebrand factor from living cells can be investigated by SICM without any
% additional labeling. , it is not always necessary to label the protein. Even with SICM alone the 
% detection of such a protein was possible, which was verified by comparing fluorescence and SICM 
% images \cite{Nashimoto2015}.
